\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-08 doc/sw-system.tex
Added RF ref to future surveys prediction, closes #100. Also fixed author names to standard ones seen on ADS.

The futuristic lens-finding problem sketched in \Sref{sec:intro}, where $10^5$
lenses are to be found in a $10^4$ square degree wide field imaging survey, is
approximately representative of the challenge facing both the LSST and Euclid
strong lensing science teams \citep{LSSTSciBook,EuclidSciBook}. What role could
citizen scientists at \SW play in lens searching in the next decade? From
\Eref{eq:speed}, and assuming $\tau_0 = 6$ days (as above), we see that for the
\SW crowd to be able to classify $10^8$ images of  photometrically-selected
massive galaxies and groups in approximately 60 days, it would need to contain
$10^7$ volunteers. This is only  a factor of ten larger than the current size of
the Zooniverse userbase. Alternatively, suppose that automated  lens finding
algorithms are able to select as few as $10^6$ targets for visual inspection (a
sample with 10\% purity). Increasing $\tau_0$ by a factor of three to allow for
more inspection time per subject,  we find that \SW could enable a crowd of just
$10^6$ volunteers to assess them in about three  weeks.

>>>>

The futuristic lens-finding problem sketched in \Sref{sec:intro}, where $10^5$
lenses are to be found in a $10^4$ square degree wide field imaging survey, is
approximately representative of the challenge facing both the LSST and Euclid
strong lensing science teams \citep{LSSTSciBook,EuclidSciBook}. What role could
citizen scientists at \SW play in lens searching in the next decade? From
\Eref{eq:speed}, and assuming $\tau_0 = 6$ days (as above), we see that for the
\SW crowd to be able to classify $10^8$ images of  photometrically-selected
massive galaxies and groups in approximately 60 days, it would need to contain
$10^7$ volunteers. This is only  a factor of ten larger than the current size of
the Zooniverse userbase. Alternatively, suppose that automated  lens finding
algorithms were able to select as few as $10^5$ targets for visual
inspection,
sample with 10\% purity with a surface density of $\sim10$ per square degree
\citep[a rate within reach of \RF, for example:][]{GavazziEtal2014}.
Increasing $\tau_0$ by a factor of three to allow for
more inspection time per subject,  we find that \SW could enable a crowd of just
$10^5$ volunteers to assess them in about three weeks.
